A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-10-29 rr-flow.Rmd
https instead of ssh closes #57

Git also makes it especially easy to share and collaborate on a project with other researchers. A popular service for sharing materials via Git is [GitHub](https://github.com). Just sharing Git repositories with the public is always free, private repositories (only visible to persons you invite) are [free for researchers](https://help.GitHub.com/en/articles/applying-for-an-educator-or-researcher-discount). After creating a user account, one can create a new repository where GitHub advises you how to upload your repository from the terminal, e.g., for our repository (here with user name 'aaronpeikert' and repository name 'reproducible-research'):

```{bash, eval=FALSE}
git remote add origin git@github.com:aaronpeikert/reproducible-research.git
git push -u origin master
```

@@

```{bash, eval=FALSE}
https://github.com/aaronpeikert/reproducible-research.git
```

>>>>

Git also makes it especially easy to share and collaborate on a project with other researchers. A popular service for sharing materials via Git is [GitHub](https://github.com). Just sharing Git repositories with the public is always free, private repositories (only visible to persons you invite) are [free for researchers](https://help.github.com/en/articles/applying-for-an-educator-or-researcher-discount). After creating a user account, one can create a new repository where GitHub advises you how to upload your repository from the terminal, e.g., for our repository (here with user name 'aaronpeikert' and repository name 'reproducible-research'):

```{bash, eval=FALSE}
git remote add origin https://github.com/aaronpeikert/reproducible-research.git
git push -u origin master
```

@@

```{bash, eval=FALSE}
git clone https://github.com/aaronpeikert/reproducible-research.git
```
